\plaintitle

### 2017-02-24 paper/paper.tex
Paper: One more paragraph to intro about expressivity \& new interfaces

>>>>

Recently, researchers suggested frameworks to assess the expressive possibilities of new interfaces for music performance \cite{Poepel2005}.
In their model, performers communicate emotions by ``coding'' them with a set of musical properties.
Specifically, they mention tempo, sound level, timing, intonation, articulation, timbre, vibrato, tone attacks, tone decays and pauses.
The listeners, on the other hand, ``decode'' these properties to understand the performer expressive intention.
This model for understanding expression in performance was validated in controlled experiment \cite{Gabrielsson1996}.
Now, new interfaces for music performance should provide the means to control these properties to allow the performer to convey emotion.
But controllability is probably not enough.
New interfaces should consider the interface ``efficiency'' - the ratio between the complexity of the resulted sound and the complexity of the controller input \cite{Jorda2004}.
In addition, the ability to master the instrument, questions of controllability versus randomness, and physical feedback should all be taken into account \cite{Dobrian2006}.
